### 2025-08-05 mixed-models.qmd
20250804 - hide chunks
20250805 - fix

load(file = "./data/nfl_depthCharts.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_weekly.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_seasonal.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/bayesianMixedModelFit.RData", fsep = ""))
```

@@

```{r}
#| label: clear-memory-bayesian1

gc()
```

```{r}
#| label: generate-model-implied-predictions-fantasy-points-by-position-age-bayesian2

@@

```{r}
#| label: clear-memory-bayesian2

gc()
```

>>>>

load(file = "./data/nfl_depthCharts.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_weekly.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_seasonal.RData", fsep = ""))

load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/bayesianMixedModelFit.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/modelPredictions_bayesian.RData", fsep = ""))
```

@@

```{r}
#| label: generate-model-implied-predictions-fantasy-points-by-position-age-bayesian2
#| eval: false

@@

save(
  modelPredictions_bayesian,
  file = "./data/modelPredictions_bayesian.RData")
```

load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/modelPredictions_bayesian.RData", fsep = ""))
```

load(file = "./data/modelPredictions_bayesian.RData")
```
